---
title: "eds212-day2-part1"
author: "Adelaide Robinson"
date: '2022-08-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Derivates in R

# find the derivative of $$f(x) = 5x^2$$

dollar signs allow blocking

```{r}
#options for derivatives
#steps : 
# write evaluated expression
#define it using the derivative function
#assign a value to x and then evaluate
#you can also create a sequence of values for x and plug it in
ex_1 <- expression( 5 * x ^ 2)
my_derivative <- deriv(ex_1 , "x")
# I want to find the slope @ x=2.8
#assign the value to x 
x <-2.8
eval(my_derivative)

```

## Find the derivative a second way

Find the slope of $g(z) = 2 z^3 -10.5z^2 +4.1$

```{r}
gz <- expression(2 * z ^ 3 -10.5 * z ^2 +4.1)
#find the derivative
dg_dz <- D(gz , "z")
#gives a simpler output
# evaluate the slope over a sequence of values
z <- seq(from = -3, to = 4 , by = 0.5)
eval(dg_dz)
```

# Notes on using github

## making a non version controlled project into a version controlled project

-   in the console type usethis::use_git make sure it is locally controlled
-   yes twice it will restart and be committed this is creating a git repository on our computer this still only exists on our computer
-   usethis::use_github, saves it on github
-   as soon as you make changes and save, you should see the file in the git tab. rmd means it has been modified
-   first send changes to local git repo, staging is the process of saying what you are ready to send to local git at this point. click on the check. and commit, add a commit message and close it
-   there is now a messae saying "your branch is ahead of origin/master by 1 commit. meaning it is only stored locally but not on github
-   we need to  **push**  these changes
-    push the upper green arrow
-    git and github are not tied to rstudio
-    one example of a workflow where you are the only one making changes 

